Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-06-28 ijar-npb-ms.tex
literature suggestions by reviewer 1

*** add references to existing work on reliability with IP, including \cite{UC07} here or in par above?***

@@

@@

To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
we now need to minimise and maximise Equation~\eqref{eq:rsyswithsurvsign} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
%It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
%as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
%
%To see this,
%remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
%From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
%%the posterior parameter set bounds are the transformed prior parameter set bounds,
%%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
%such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
%%
%Now, a higher posterior expected functioning probability means
%higher probability for many components out of $m_k$ surviving,
%i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
%Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
%its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
%such that the cmfs for different values of $\yktn$ do not cross each other.
%This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
%such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
%For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
%thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
%which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
We therefore have
%
%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.
%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktz, \nktz, s^k_t) \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                         {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \,, \label{eq:LwrSysPostA}
\end{align}
and similarly maximising for $\uRsys(\cdot)$.

>>>>

@@

In contrast to previous work on reliability with IP, our focus is on learning component reliabilities***

*** add references to existing work on reliability with IP, including \cite{UC07} here ***

\cite{2011:antonucci::noisyor}

@@

To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
we now need to minimise and maximise Equation~\eqref{eq:rsyswithsurvsign} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
%It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
%as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
%
%To see this,
%remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
%From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
%%the posterior parameter set bounds are the transformed prior parameter set bounds,
%%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
%such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
%%
%Now, a higher posterior expected functioning probability means
%higher probability for many components out of $m_k$ surviving,
%i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
%Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
%its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
%such that the cmfs for different values of $\yktn$ do not cross each other.
%This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
%such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
%For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
%thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
%which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
We therefore have
%
%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.
%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktz, \nktz, s^k_t) \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                         {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \,, \label{eq:LwrSysPostA}
\end{align}
and similarly maximising for $\uRsys(\cdot)$.
In doing so, we assume components of the same type $k$ to be exchangeable given $\PtZi{k}$
\citep[see][\S 3.4 on extending exchangeability to imprecise probability]{itip},
and components of different types to follow \emph{strong independence}
\citep[see][\S 3.2.4]{itip}.
